---
title: "EDA wine prices"
output: html_notebook
---


```{r}
library(data.table)

dt <- fread('winemag-data_first150k.csv')
head(dt)
```
## Data cleaning

First, we want to drop any columns we're not interested in. In this analysis, we will focus only on:
- points
- price
- country
- province
- variety

We're omitting any other variables since we don't need them to answer this question. 

We also need to drop any data where we don't have prices and impute any missing data (or drop it). 

```{r}
dt <- dt[!is.na(price),c('points', 'price', 'province', 'country', 'variety')]

summary(dt)
```


## EDA 

Second, we will look into the dataset. How many observations? How many different regions? Is there enough between regions and varietals of wine? What about the relationship between `points` and `price`? 

Overall, we're trying to find out _what are some good predictors_ for the price of each wine bottle. 
```{r}
plot(price ~ points, data = dt)
plot(jitter(log(price)) ~ points, data = dt) # the relationship looks more linear if we plot the logs
```

We see from the above that there is a positive relationship between points and price for a bottle of wine. However, for higher points, we are seeing a larger variation of prices, and interestingly, for wines with 100 points, we have much fewer data points, and also the prices we see are somewhat lower than for lower prices. 

What about the relationship between `price` and the region on the varietal?

```{r}
dt[!is.na(price)]
```

